%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Albert Lea School System} % Organization
    {School Teacher} % Job title
    {Albert Lea, Minnesota} % Location
    {Aug 2022 - May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created \href{https://github.com/asamwow/introduction-to-programming}{my own curriculum} by using Emacs presentation software to help introduce text based programming to middle school students.}
        \item {Worked as a team to support children with ASD by developing patience and empathy.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Stratagem Group} % Organization
    {Software Developer} % Job title
    {King of Prussia, Pennsylvania} % Location
    {Jan 2022 - Apr 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Automated development pipeline from story start to finish
               with makefiles, systemd unit files, and literate org-mode markdown documentation
               all generated with elisp scripts.}
      \end{cvitems}
    }

%---------------------------------------------------------
  %% \cventry
  %%   {Mathnasium} % Organization
  %%   {Math Tutor} % Job title
  %%   {Rosemont/Blue Bell, Pennsylvania} % Location
  %%   {Dec. 2021 - Apr 2022} % Date(s)
  %%   {
  %%     \begin{cvitems} % Description(s) of tasks/responsibilities
  %%       \item {Understand students perspective by being a patient listener to understand how to help them best.}
  %%       \item {Encourage general understanding of concepts by asking many questions and creating unique problems or diagrams.}
  %%     \end{cvitems}
  %%   }

%---------------------------------------------------------
  \cventry
    {Independent} % Organization
    {Game Developer} % Job title
    {King of Prussia, Pennsylvania} % Location
    {Summer 2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {See my current project, \url{http://castles.life}. Reach out for a free game key.}
        \item {Realtime, self hosted infinite 3D world streamed asynchronously to multiple unity client.}
        \item {Client shares class library with entity framework server to send and receive minimized byte messages for great development velocity.}
        \item {Highly custom features such as local development support, test scenario creator, and a featherlight codebase that deploys in seconds.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lockheed Martin - Space} % Organization
    {Software Engineer Asc.} % Job title
    {King of Prussia, Pennsylvania} % Location
    {Sept. 2020 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Battled with the complexity of maintaining a large codebase by sifting through hundreds of thousands of lines of code and logs shown by my exceptional adherence to existing architecture.}
        \item {Automated development procedures such as kubernetes and gitlab pipelines with makefiles, bash, and python scripts.}
        \item {Worked with my team to accomplish goals shown by my feature level improvements within time limitations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {HVH Precision Analytics} % Organization
    {Web Developer} % Job title
    {Wayne, Pennsylvania} % Location
    {Nov. 2019 - Apr. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with Amazon AWS resources to query medical patient data and run analytics.}
        \item {Helped develop localized testing environment with mimicked network connections and user inputs.}
        \item {Made several required full-stack changes to client web access portal using Dotnet, SQL, and Vue.js.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mathnasium/Private Lessons} % Organization
    {Math Tutor} % Job title
    {Menomonie, Wisconsin} % Location
    {Mar. 2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Understand students perspective by being a patient listener to understand how to help them best.}
        \item {Encourage general understanding of concepts by asking many questions and creating unique problems or diagrams.}
        \item {Displayed skills in calculus and linear algebra by breaking down advanced mathematical concepts to a less technical audience.}
      \end{cvitems}
    }

%% %---------------------------------------------------------
%%   \cventry
%%     {Shotgun Express, Inc}
%%     {Web Developer}
%%     {Twin Cities, Minnesota} % Location
%%     {Fall 2018} % Date(s)
%%     {
%%       \begin{cvitems} % Description(s) of tasks/responsibilities
%%         \item {Independently created JavaScript app to calculate price of delivering various shipping pallets to various places around the twin cities. Prices are retrieved automatically from a Google spreadsheet to allow non-technical personnel to edit prices when needed. Removed the need to reference several tables to find the correct price, dramatically improving the efficiency of the operation.}
%%       \end{cvitems}
%%     }

%---------------------------------------------------------

\end{cventries}
